---
title: "Cabbages"
author: "Rita Jarbanda"
date: "Fall 2023"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results
```{r}
plot(VitC~Cult,data= veggy, main="Vitaim-C Contents by Cultivation method")
```
<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results
```{r}
favstats(VitC~Cult,data=veggy)
```
The data Shows that Q3 of C39 is smaller than Q1 of C52 indicating that they are indeed disjoint

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Inferential Results
```{r}
t.test(VitC~Cult,data=veggy)
```
The p-value 0.000000003405. This clearly shows C39 and C52 are very different from each other 
<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
I used the Numerical~cat helper file since Chatgpt was giving me a hard time doing it. I find that the helper file are just easy and ore stright foward to use then chatgpt.
After reviewing my data, it showed me that Q3 of C39 is smaller than Q1 of C52 indicating that they are indeed disjoint
The next step I took was to make a t test plot and that showed me that the p Value was  p-value 0.000000003405. This shows C39 and C52 are very different from each other 